The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-28 paper.Rmd
updated some formatting

Therefore, this simulation involves four species: pyrimidine monomers Thymine 1 (\( T1 \)), Thymine 2 (\( T2 \)), and dimer photoproducts \( CPD \) and \( 64PP \); and two reactions channels: \( c1 \) and \( c2 \).
\[
T1 + T2 \xrightarrow{c1} CPD
\]
\[
T1 + T2 \xrightarrow{c2} 64PP
\]

We will simulate the dimerization of thymine using propensity based on the formation yield of CPD (~37 per 10^6 normal bases) and 64-PP (~2 per 10^6 normal bases) found by exposing skin cells to a UVB dose of 0.2 J/cm^2 (@Mouret2006). As the amount of thymine bases in DNA varies from person to person, we will simulate thymine photodimerization of 1000 pairs of thymine.

>>>>

Therefore, this simulation involves four species: pyrimidine monomers Thymine 1 (\( T_1 \)), Thymine 2 (\( T_2 \)), and dimer photoproducts \( CPD \) and \( 64PP \); and two reactions channels: \( c_1 \) and \( c_2 \).
\[
T_1 + T_2 \xrightarrow{c_1} CPD
\]
\[
T_1 + T_2 \xrightarrow{c_2} 64PP
\]

We will simulate the dimerization of thymine using propensity based on the formation yield of CPD (~37 per \(10^6\) normal bases) and 64-PP (~2 per \(10^6\) normal bases) found by exposing skin cells to a UVB dose of 0.2 \(J/cm^2\) (@Mouret2006). As the amount of thymine bases in DNA varies from person to person, we will simulate thymine photodimerization of 1000 pairs of thymine.
